Flatiron cleaning

### 2022-03-03 Rmd/rdi analysis.Rmd
Add carbo only adjusted HR

@@

>>>>

### Carbo only
`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking`
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology`
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

@@

## Carbo only
`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking`
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%

  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
             ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology`
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>
